New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-04 Manuscript/Manuscript.tex
Manuscript format
Starting with M&M

\section{Content section one}

\subsection{Subsection Heading Here}

Subsection text here.

\subsubsection{Subsubsection Heading Here}

@@

\section{Content section with citations}

@@

Copernicus supports biblatex and a sample bibliography is in file
\texttt{sample.bib}. Read \citep{Feynman1963118}, and
\citep[see][]{Dirac1953888}.

@@

\section{Content section with list}

@@

@@

The conclusion goes here. You can modify the section name with
\texttt{\textbackslash{}conclusions{[}modified\ heading\ if\ necessary{]}}.

\codedataavailability{R code and data set used in this work is available
at
https://github.com/EcoComplex/WeddellSea} %% use this section when having data sets and software code available

@@

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{WeddellSea.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

>>>>

The objective of this work is twofold: 1) estimate the interaction
strength of the Weddell Sea food web, and 2) determine key trophic
species considering its influence on the stability of the network.

\section{Methodology}

\subsection{Study area}

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
with a length of approximately 450 km. Water depth varies from 200 to
500 m. Shallower areas are covered by continental ice, which forms the
coastline along the eastern and southern part of the Weddell Sea. The
shelf area contains a complex three-dimensional habitat with large
biomass, intermediate to high diversity in comparison to benthic boreal
communities and a spatially patchy distribution of organisms
\citep[\citet{Teixido2002}]{Dayton1990}.

\subsection{Data source}

@@

\section{Results}

@@

Copernicus supports biblatex and a sample bibliography is in file
\texttt{WeddellSea.bib}. Read \citep{Pawar2012}, and
\citep[see][]{Dirac1953888}.

@@

\section{Discussion}

@@

\begin{verbatim}
## tlmgr update --all --self
\end{verbatim}

\begin{verbatim}
## tlmgr install algorithms algorithmicx
\end{verbatim}

@@

The conclusion goes here.

@@

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{../WeddellSea.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}
